Addressing climate change and development pressures in an urban estuary through habitat restoration planning

### 2022-08-22 manu-draft.qmd
subtidal habitat change table

execute: 
  echo: false
  warning: false
---

```{r, results = 'hide'}
library(knitr)
library(here)
```

@@

@@

Table 1: Land use change table

Table 2: Subtidal change table

>>>>

execute: 
  echo: false
  warning: false
  ft.keepnext: false
  ft.align: left
---

```{r, results = 'hide'}
library(knitr)
library(here)
library(flextable)
library(dplyr)
library(officer)
library(officedown)

load(file = here('tabs/subttab.RData'))
```

@@

Table 1

@@

```{r}
#| tbl-cap: Change over time in hectares for subtidal habitats in Tampa Bay.  Columns show years with available data and the final two columns show the change and percent change from 1988 to 2018.  Oyster bars were not meaningfully quantified prior to 2014. 
subttab
```

Table 2: Land use change table
